---
title: "index"
output: html_document
---

```{r, echo=FALSE, message=FALSE}
library(dplyr)
library(plotly)
library(knitr)
setwd("/Users/LukeCommins/Documents/info498f/a7cool_beanz/scripts/")
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")
source("summary_function.R")
list <- write_summary(data)
```

#Informatics 498f Infomation

Welcome to info498f where we have `r list$num_freshman` freshman, `r list$num_sophomore` sophomores, `r list$num_junior` juniors, 
and `r list$num_seniors` seniors.  We learn and perform various tasks using R.  However, we use different operating systems to do these tasks.  Here is that information visualized in total and by class:

```{r, echo=FALSE, message=FALSE}
setwd("/Users/LukeCommins/Documents/info498f/a7cool_beanz/scripts/")
source("os_user_info.R")
os_user_total_info(data)
os_user_by_class(data)
```

Now let's look at the experience level of the class:

```{r, echo=FALSE, message=FALSE}
setwd("/Users/LukeCommins/Documents/info498f/a7cool_beanz/scripts/")
source("chart_2.R")
chart_2(data)
```

Have a nice day!
